Age-related changes in plant growth and traits

### 2016-10-26 scripts/Accessory_figs_20160905.Rmd
small changes

plot(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col="#0571b0",ylim=c(-0.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col="#ca0020")
extra.top.left.logx("d",2,1)
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop total pollen-attraction investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("successful ovules","aborted ovules"),col=c("#0571b0","#ca0020"),pch=c(16,16),bty="n",cex=0.7)

@@

#Table with above model results
```{r}
mod_prop_prepollen_costs <- sma(prop_prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")

>>>>

plot(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],pch=16,log="x",col="#0571b0",ylim=c(-.1,1.1),xlim=c(.01,100),xlab="",ylab="",xaxt="n",yaxt="n")
points(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],pch=16,col="#ca0020")
extra.top.left.logx("d",2,1)
axis(2, at=c(0,.2,.4,.6,.8,1), labels=c(0,0.2,0.4,0.6,0.8,1),cex.axis=0.8,las=2)
axis(1, at=c(0.01,1,100), labels=c(0.01,1,100),cex.axis=0.8)
mtext("seed size (mg)",1,line=1.8,cex=0.7)
mtext("prop total pollen-attraction investment",2,line=2.3,cex=0.7)
legend("bottomleft",legend=c("successful ovules","aborted ovules"),col=c("#0571b0","#ca0020"),pch=c(16,16),bty="n",cex=0.7)

@@

#Table with above model results
```{r}
mod_prop_prepollen_costs <- sma(prop_prepollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_postpollen_costs <- sma(prop_postpollen_costs~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_prepollen_success <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_prepollen_success_SMA <- sma(prop_prepollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="SMA")
mod_prop_prepollen_failure <- sma(prop_prepollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_postpollen_success <- sma(prop_postpollen_success~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
mod_prop_postpollen_failure <- sma(prop_postpollen_failure~embryo_endo_size,SummarySpp[["mean"]],log="x",method="OLS")
